Limited predictability of amino acid substitutions in seasonal influenza viruses

### 2020-12-07 article.tex
Updated diff.tex

These models are not meant to be accurate models of influenza viruses evolution. 
But figure~\sref{fig:simulations} does show is that the patterns observed in influenza virus evolution are only reproduced by models of adapting populations when pushing clonal competition to extreme values.
We conclude that the pattern in figure~\ref{fig:fix_loss_active} may not be a straightforward manifestation of genetic linkage and clonal interference, but that some more intricate interplay of epidemiology, seasonality, human immunity and chance gives rise to the weakly predictable yet strongly selected evolutionary dynamics of IAVs.

>>>>

These models are not meant to be accurate models of influenza viruses evolution. 
But figure~\sref{fig:simulations} does show that the patterns observed in influenza virus evolution are only reproduced by models of adapting populations when pushing clonal competition to extreme values.
We conclude that the pattern in figure~\ref{fig:fix_loss_active} may not be a straightforward manifestation of genetic linkage and clonal interference, but that some more intricate interplay of epidemiology, seasonality, human immunity and chance gives rise to the weakly predictable yet strongly selected evolutionary dynamics of IAVs.
